Technical Report

### 2024-06-25 Reports/tech_report1.tex
update report

>>>>

\subsection*{CURRENT or ALL}

After a few tests, we decide to only use ALL-ALL for all cases: For length 3 part, we find ALL is significantly better; For length 4 part, ALL-ALL are the easiest to implement, and do not lose accuracy.

\section{New Bootstrap Form}

\section{Large test of layer 3 and layer 5 of 1023 cases}

These tests consist of several parts: layer 3, layer 5 mixed 1 and 2, layer 5 open only layer 3, layer 5 open layer 1.

\subsection*{Basic Scheme of tests}

In each test, first use the standard/quick method to choose first 50/70 nodes for target layer. Then group 50/70 nodes in 10 groups. In $2^10-1$ cases, use corresponding nodes to open.

The value $Imp(a,a',\cdots)$ of nodes $a,a',\cdots$ is the difference of average uncertainty of LP model and the model when only open nodes $a,a',\cdots$: Let $A=\{a,a',\cdots\}$, then $$Imp(A)=LP-MILP_A.$$

The finding of these tests is that: $$Imp(A)\approx \sum_{a\in A} Imp(a).$$ We use $\dfrac{\sum_{a\in A} Imp(a)}{Imp(A)}$ to check how close they are.

For each case $A_0$, its error means $$|\dfrac{\sum_{a\in A_0} Imp(a)}{Imp(A_0)}-Average_{A} \dfrac{\sum_{a\in A} Imp(a)}{Imp(A)}|.$$

\subsection*{Layer 3}

In the case, we open nodes in layer 1.

The average quotient is 0.9893127409573279. The error is very small: in all 1023, no error is greater than 1\%.

\subsection*{Layer 5, only open in layer 3}

In this case, we open nodes in layer 3.

The average quotient is 0.9930808321092559. The error is also very small: in all cases, the max error is 1.042\%.

\subsection*{Layer 5, only open in layer 1}

From now, the error and average become not so good. The average quotient is 0.9027497392008165, and the standard deviation of error is 3.01\%, the max error is about 10\%.

\subsection*{Layer 5, both in layer 1 and layer 3}

The error and average are still not so good. The average quotient is 0.8951295616274486, and the standard deviation of error is 3.7\%, the max error is about 10\%.

From this we can guess that the error is mostly caused by nodes in layer 1 rather than layer 3.
